Clearance Project - 1 - Data Generation

### 2025-03-17 data-raw/ClearanceProject-1-DataRmd.Rmd
Updated some data scripts and files to ensure we have both rat and human fup and Clint data.

```{r chemical-lists}
member_list <- list(
  httk_3comp2 = unique(get_cheminfo(info = "DTXSID",
                                species = "human",
                                model = "3compartment2",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings(),
  cvt = cvt %>% 
    filter(species %in% c("human", "rat"),
           conc_medium_normalized == "plasma") %>%
    pull(analyte_dtxsid)
)
# These are the chemicals we can evaluate!
target_chems <- intersect(member_list$cvt, member_list$httk_3comp2)
all_chems <- member_list$httk_3comp2

# save in an .Rdata file
save(target_chems, all_chems,
     file = "data-raw/chem_lists.RData")

@@

```{r getting_curent_params}

# rat_pars_rat <- parameterize_rat()
rat_pars_human <- parameterize_rat(human_clint_fup = TRUE)
#human_pars_human <- parameterize_human()
chosen_list <- rat_pars_human
# The following are derived from the above selected list (see environment)
this_param_rest_l <- chosen_list$named_params_restrictive
this_param_nrest_l <- chosen_list$named_params_nonrestrictive
this_param_df <- chosen_list$param_df
this_httk_clearance_df <- chosen_list$clearance_df

# HTTK predictions

# Predictions from httk(code retained but not run after 2.20.2025)
restrictive_preds <- get_httk_preds(
  parameters = this_param_rest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_restrictive"),
  .cols = starts_with("httk_")
)

nonrestrictive_preds <- get_httk_preds(
  parameters = this_param_nrest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_nonrestrictive"),
  .cols = starts_with("httk_")
)

@@

all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) %>%
  filter_targets()
rm(restrictive_preds, nonrestrictive_preds)

this_css_df <- inner_join(
  css_httk_batch(this_param_rest_l, restrictive = TRUE),
  css_httk_batch(this_param_nrest_l, restrictive = FALSE)
) %>% filter_targets()

this_clint_df <- data.frame(Chemical = names(this_param_rest_l),
                            CLint = vapply(names(this_param_rest_l),
                                           \(x) {
                                             this_param_rest_l[[x]][["Clint"]]
                                           },
                                           FUN.VALUE = numeric(1L)
                            ))

save(this_param_rest_l, this_param_nrest_l,
     this_param_df, this_httk_clearance_df,
     all_httk_preds, this_css_df, this_clint_df,
     file = "data-raw/rat_pars_human.RData")
```

>>>>

```{r chemical-lists}
human_3compchems <- unique(get_cheminfo(info = "DTXSID",
                                species = "human",
                                model = "3compartment2",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings()

rat_3compchems <- unique(get_cheminfo(info = "DTXSID",
                                species = "rat",
                                model = "3compartment2",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings()

cvt_plasma_chems <-  cvt %>% 
    filter(species %in% c("human", "rat"),
           conc_medium_normalized == "plasma") %>%
    pull(analyte_dtxsid)

# These are the chemicals we can evaluate!
target_chems_human <- intersect(cvt_plasma_chems,
                                human_3compchems)
target_chems_rat <- intersect(cvt_plasma_chems,
                              rat_3compchems)

# save in an .Rdata file
save(target_chems_human, target_chems_rat, 
     human_3compchems, rat_3compchems,
     file = "data-raw/chem_lists.RData")

@@

```{r getting_curent_params_rpr}

rat_pars_rat <- parameterize_rat(human_clint_fup = FALSE)

rpr_param_rest_l <- rat_pars_rat$named_params_restrictive
rpr_param_nrest_l <- rat_pars_rat$named_params_nonrestrictive
rpr_param_df <- rat_pars_rat$param_df
rpr_httk_clearance_df <- rat_pars_rat$clearance_df

# HTTK predictions
# Predictions from httk(code retained but not run after 2.20.2025)
restrictive_preds <- get_httk_preds(
  parameters = rpr_param_rest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_restrictive"),
  .cols = starts_with("httk_")
)

nonrestrictive_preds <- get_httk_preds(
  parameters = rpr_param_nrest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_nonrestrictive"),
  .cols = starts_with("httk_")
)

@@

rpr_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) 
rm(restrictive_preds, nonrestrictive_preds)

rpr_css_df <- inner_join(
  css_httk_batch(rpr_param_rest_l, restrictive = TRUE),
  css_httk_batch(rpr_param_nrest_l, restrictive = FALSE)
)

rpr_clint_df <- data.frame(Chemical = names(rpr_param_rest_l),
                           CLint = vapply(names(rpr_param_rest_l),
                                          \(x) {
                                            rpr_param_rest_l[[x]][["Clint"]]
                                          },
                                          FUN.VALUE = numeric(1L)
                           ))

save(rpr_param_rest_l, rpr_param_nrest_l,
     rpr_param_df, rpr_httk_clearance_df,
     rpr_httk_preds, rpr_css_df, rpr_clint_df,
     file = "data-raw/rat_pars_rat.RData")
```

```{r getting_current_params_rph}

rat_pars_human <- parameterize_rat(human_clint_fup = TRUE)
#human_pars_human <- parameterize_human()
# The following are derived from the above selected list (see environment)
rph_param_rest_l <- rat_pars_human$named_params_restrictive
rph_param_nrest_l <- rat_pars_human$named_params_nonrestrictive
rph_param_df <- rat_pars_human$param_df
rph_httk_clearance_df <- rat_pars_human$clearance_df

# HTTK predictions
# Predictions from httk(code retained but not run after 2.20.2025)
restrictive_preds <- get_httk_preds(
  parameters = rph_param_rest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_restrictive"),
  .cols = starts_with("httk_")
)

nonrestrictive_preds <- get_httk_preds(
  parameters = rph_param_nrest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_nonrestrictive"),
  .cols = starts_with("httk_")
)

rph_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds)
rm(restrictive_preds, nonrestrictive_preds)

rph_css_df <- inner_join(
  css_httk_batch(rph_param_rest_l, restrictive = TRUE),
  css_httk_batch(rph_param_nrest_l, restrictive = FALSE)
)

rph_clint_df <- data.frame(Chemical = names(rph_param_rest_l),
                            CLint = vapply(names(rph_param_rest_l),
                                           \(x) {
                                             rph_param_rest_l[[x]][["Clint"]]
                                           },
                                           FUN.VALUE = numeric(1L)
                            ))

save(rph_param_rest_l, rph_param_nrest_l,
     rph_param_df, rph_httk_clearance_df,
     rph_httk_preds, rph_css_df, rph_clint_df,
     file = "data-raw/rat_pars_human.RData")
```
